### 2020-02-05 ncov.tex
typo
tweak again

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have focused on estimating the basic reproductive number \Ro, the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro vary widely, despite relying on similar data sources.
Here, we present a framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We then apply our framework to early estimates of \Ro for the 2019-nCoV outbreak, estimating the \Ro from the pooled distribution as 2.9 (95\% CI: 2.1-4.5).
Our results emphasize the importance of propagating propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution in efforts to estimate \Ro at the outset of an epidemic.

\swp{JSW suggests including our pooled estimate of R in the abstract. Not sure if we want that.}
\swp{DJDE suggests using overline G rather than bar G. I think overline looks ugly.}

@@

In this study, we focused on propagating errors arising from implicit or explicit estimates of growth rate and generation intervals.
Other key issues underlying early estimates of \Ro include statistical independence and types of noise.
\jsw{Why is this here? Fine sentence, but belongs 2 paragraphs down and is largely redundant.}
\swp{I proprose we drop these two sentences.}

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As the epidemic progresses, many disease modelers have focused on estimating the basic reproductive number \Ro, the average number of secondary cases caused by a primary case in an otherwise susceptible population.
The modeling approaches and resulting estimates of \Ro vary widely, despite relying on similar data sources.
Here, we present a framework for comparing and combining different estimates of \Ro across a wide range of models by decomposing the basic reproductive number into three key quantities: the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$.
We then apply our framework to early estimates of \Ro for the 2019-nCoV outbreak\jsw{, estimating the \Ro from the pooled distribution as 2.9 (95\% CI: 2.1-4.5)}.
Our results emphasize the importance of propagating propagating uncertainties in all components of \Ro, including the shape of the generation-interval distribution in efforts to estimate \Ro at the outset of an epidemic.

\swp{JSW suggests including our pooled estimate of R in the abstract. Not sure if we want that. The pooled estimates have some caveats and they're based on very early estimates. I think it's OK to leave them out.}
\swp{DJDE suggests using overline G rather than bar G. I think overline looks ugly.}

@@

In this study, we focused on propagating errors arising from implicit or explicit estimates of growth rate and generation intervals.
Other key issues underlying early estimates of \Ro include statistical independence and types of noise.
\jsw{Why is this here? Fine sentence, but belongs 2 paragraphs down and is largely redundant.}
\swp{I propose we drop these two sentences.}
